% !TEX program = pdflatex
\begin{abstract}
The software aim to help the staff of an hotel to manage the rooms of the structure.

It will help to identify free rooms in a particular period of time thus helping to understand if it is possible to satisfy clients' requests.

Also it will keep count of how many days a particular client has been host of the structure helping the manager to bill accordingly.
\end{abstract}

\section{Assigment I}

\subsection{Name}
Hotel Revolution 2014s

\subsection{Team Member}
Giovanni Pelosi, Sara Zanzottera, Gianpaolo Branca and Simone Mosciatti

\subsection{Specification}
The system will be a Back-Office information system.
The system implement the functions of a Decision Support System, it will help decide what room offer to who.

\subsection{Problem the software will solve}
How to manage the booking of rooms in a big hotel, including the assigment of rooms to big groups or guest with particular request (smokers, pets, disabilities, etc...)

\subsection{Requirements of the system}
The system helps in a useful and friendly way the staff in the hotel managment.

\begin{itemize}

\item Will allow the reception to be quick and extremely precise in answering any inquiry from possible guests.

\item Will let fast booking operation by the hotel staff.

\item Will show all the possible options available for a guest.

\item Will let the staff know who is guesting in a particular room.

\item Will let the staff know how long a guest has been in the hotel.

\item Will let the staff know which rooms will be free sooner.

\item Will help to manage the revenue of the hotel, providing an interface that shows the distribution of the bookings during the years.

\item Will provide two level of authentication, one from the staff and one from the manager, the manager will be able to access all the information while some sensitive information (revenue) won't be show to the staff.

\end{itemize}

\subsection{User}

The software will be used by the hotel staff, in particular by the receptionist and the manager.

The main user is know, and it will be possible to teach the staff how to use it.

Despite, the interface will be user friendly even for non-technical staff, so it will be simple for a new hire to learn quickly how to interact with the system.

The receptionist will, mainly, use the system to check the availability of the rooms in a specific period.

The manager will use the software to bill the client.

\subsection{Note for development}

Since the team is not extremely aware of the mechanics behind an hotel, we will ask to a real hotel staff feedback on the prototype of the software.

